The \dealii{} Library, Version 9.3

### 2021-03-10 9.3/paper.tex
Adjust funding

M.~Kronbichler was supported by the German
Research Foundation (DFG) under the project ``High-order discontinuous
Galerkin for the exa-scale'' (\mbox{ExaDG}) within the priority program ``Software
for Exascale Computing'' (SPPEXA) and the Bayerisches Kompetenznetzwerk
f\"ur Technisch-Wissen\-schaft\-li\-ches Hoch- und H\"ochstleistungsrechnen
(KONWIHR) in the context of the project
``Performance tuning of high-order discontinuous Galerkin solvers for
SuperMUC-NG''.

>>>>

M.~Kronbichler was partially supported by the
Bayerisches Kompetenznetzwerk
f\"ur Technisch-Wissen\-schaft\-li\-ches Hoch- und H\"ochstleistungsrechnen
(KONWIHR) in the context of the projects
``Performance tuning of high-order discontinuous Galerkin solvers for
SuperMUC-NG'' and ``High-order matrix-free finite element implementations with
hybrid parallelization and improved data locality''.
